\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{margin=1in}

\title{Redstone: The F***ing Manual}
\author{IriThePone}

\begin{document}
\maketitle
\pagebreak
\tableofcontents
\pagebreak

\section{Introduction}
A PDF guide to redstone.
\pagebreak

\section{Redstone Components}
Various components that create, transmit, and/or respond to redstone signals.  
\subsection{Transmission Components}
Parts that take a redstone signal and direct it to another location.
\subsubsection{Redstone Dust}
\subsubsection{Redstone Torch}
\subsubsection{Redstone Repeater}
\subsubsection{Redstone Comparator}

\pagebreak

\subsection{Digital Input Components}
Parts that create a redstone signal, either in response to a player or the envionment.
\subsubsection{Lever}
\subsubsection{Buttons}
\subsubsection{Pressure Plates}
\subsubsection{Tripwire Hook}
\subsubsection{Daylight Sensor}
\subsubsection{Observer Block}

\pagebreak

\subsection{Analog Input Components}
Parts that create an analog signal 
\subsubsection{Containers}
\subsubsection{Iron Pressure Plate}
\subsubsection{Gold Pressure Plate}
\subsubsection{Item Frame}
\subsubsection{Jukebox}
\subsubsection{Cauldron}

\pagebreak

\subsection{Container Components}
Parts related to the transportation of items between containers.
\subsubsection{Hopper}
\subsubsection{Chests}
\subsubsection{Furnace}
\subsubsection{Dispenser}
\subsubsection{Dropper}
\subsubsection{Brewing Stand}

\pagebreak

\subsection{Piston Components}
\subsubsection{Piston}
\subsubsection{Sticky Piston}
\subsubsection{Slime Block}
\subsubsection{Redstone Block}
\subsubsection{Observer Block}

\pagebreak

\subsection{Other Output Components}
Miscellaneous Parts that respond to redstone signals.
\subsubsection{Doors}
\subsubsection{Trapdoors}
\subsubsection{Fence Gates}
\subsubsection{Redstone Lamp}
\subsubsection{Note Block}

\section{Redstone Circuits}
Structures used to manipulate redstone signals.

\section{Redstone Mechanisms}
Structures used to preform a specific task.

\subsection{Hopper Shop 1:1}

\subsection{Hopper Shop 1:n}

\subsection{Hopper Shop n:1}

\subsection{Hopper Shop n:m}

\subsection{name}

\end{document}
